Predicting the 2024 US Presidential Election: A Polling-Based Forecast

### 2024-10-27 paper/paper.qmd
update model plot

library(tidyverse)
library(arrow)
library(kableExtra)
library(ggplot2)
library(dplyr)
```

@@

>>>>

library(tidyverse)
library(arrow)
library(kableExtra)
library(ggplot2)
library(dplyr)
library(rstanarm)
library(modelsummary)
```

@@

```{r}
#| echo: false
#| eval: true
#| label: fig-final
#| fig-cap: ddd
#| warning: false
#| message: false
library(modelsummary)
library(modelr)
analysis_data <- analysis_data |>
  add_predictions(model_final_glm, var = "final")

ggplot(analysis_data, aes(x = end_date)) +
  geom_point(aes(y = pct), color = "black") +
  geom_smooth(aes(y = final), color = "red", linetype = "dotted") +
  theme_classic() +
  labs(y = "Trump Percent", x = "Date", title = "Linear Model: pct ~ end_date + numeric_grade")
```

```{r, fig.pos= 'H', fig.width=10, fig.height=6}
#| echo: false
#| eval: true
#| label: fig-bayes
#| fig-cap: Poll Percentage over Time with Bayesian Fit
#| warning: false

new_data <- data.frame(
  end_date = seq(
    min(analysis_data$end_date),
    max(analysis_data$end_date),
    length.out = 100
  ),
  numeric_grade = mean(analysis_data$numeric_grade),
  pollscore = mean(analysis_data$pollscore),
  transparency_score = mean(analysis_data$transparency_score),
  pollster = factor("AtlasIntel")
)

posterior_preds <- posterior_predict(model_bayes, newdata = new_data)

pred_summary <- new_data |>
  mutate(
    pred_mean = colMeans(posterior_preds),
    pred_lower = apply(posterior_preds, 2, quantile, probs = 0.025),
    pred_upper = apply(posterior_preds, 2, quantile, probs = 0.975)
  )

ggplot(analysis_data, aes(x = end_date, y = pct, color = pollster)) +
  geom_point() +
  geom_line(
    data = pred_summary,
    aes(x = end_date, y = pred_mean),
    color = "blue",
    inherit.aes = FALSE
  ) +
  geom_ribbon(
    data = pred_summary,
    aes(x = end_date, ymin = pred_lower, ymax = pred_upper),
    alpha = 0.2,
    inherit.aes = FALSE
  ) +
  labs(
    x = "End Date",
    y = "Percentage"
  ) +
  theme_minimal() +
  theme(
    legend.key.size = unit(1, "cm"),  # 图例项的大小
    legend.text = element_text(size = 5)  # 图例文字的大小
  )
```
